Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey

### 2017-08-23 cloverflow_technical_report/cloverflow_survey_rn.tex
Another update to the technical report.

\newcommand\fscore{\operatorname{F-score}}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{float}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{algorithm}
%\usepackage{cleveref}
\usepackage{algpseudocode}
\usepackage{pifont}
%\usepackage{cite}
\usepackage{verbatim}
\usepackage{url}
%\usepackage{microtype}
\usepackage{caption}
\usepackage{booktabs} % For formal tables
\usepackage{subcaption}
\usepackage[misc,geometry]{ifsym} 
\usepackage{etoolbox}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}

@@

\author{Chaiyong~Ragkhitwetsagul, Jens~Krinke, Mathues~Paixao,~Giuseppe Bianco, Rocco~Oliveto}

@@

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to software licensing conflicts):} \textit{are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
	\item \textbf{RQ4 (Awareness of Stack Overflow visitors to outdated code):} \textit{are Stack Overflow visitors aware of outdated code on Stack Overflow?}
	\item \textbf{RQ5 (Awareness of Stack Overflow visitors to software licensing conflicts):} \textit{are Stack Overflow visitors aware of of software licensing conflicts caused by reusing code snippets from Stack Overflow?}
\end{enumerate}

\section{Research Methodology}
The study is performed using online surveys. We designed the surveys using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. The
surveys are completely anonymous and the participants could decide to leave at
any time. They do not collect any sensitive personal information from the
participants and were approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at UCL.  The complete versions of
both surveys can be found in the Appendix A and B.

@@

\subsection{The Answerer Survey}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions were mandatory while the other 9 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, experience of
answering Stack Overflow questions, sources of the Stack Overflow snippets,
concerns of copying code snippets to Stack Overflow, problems from code 
snippets on Stack Overflow, fixing outdated code, and additional feedbacks.

@@

\subsection{The Visitor Survey}

The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
questions. The first four questions were mandatory while the other 12 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, importance of
Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
Stack Overflow snippets, licensing of code on Stack Overflow, and additional
feedbacks.

\begin{table}
	\centering
	\caption{The Stack Overflow visitors taken the survey}
	\label{tab:visitors}
	\begin{tabular}{lr}
		\toprule
		Invitation channels & Answers \\
		\midrule
		Chaiyong's Facebook post & 47 \\
		Blognone.com & 32 \\
		University of Molise & 6 \\
		comp.lang.java.programmer & 3 \\
		Software Engineering Facebook page & 1 \\
		\midrule
		Total & 89 \\
		\bottomrule
	\end{tabular}
\end{table}

The participants for this survey were invited to take the survey via five
channels. The first channel is via the first author's Facebook post where the
first author invited friends who are software developers and have experience of
copying code snippets from Stack Overflow to take the survey. The second channel
is a popular Thai technology news and media community called blognone.com which
attracts a high number of software developers. The first author posted an
invitation to the visitor survey in a discussion forum. The third channel
collects answers from University of Molise which is the third author's
workplace. The last two channels are from a comp.lang.java.programmer Google
groups and Software Engineering Facebook page. The survey was open for
participation for a month, from 25 July 2017 to 25 August 2017, before we
collected and analysed the responses. The number of participants taken the
survey are shown in Table~\ref{tab:visitors}.

@@

\subsection{Answerer Responses}
We received 113 answers (38\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For research question 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time. Other less popular choices include copying code from their personal projects, and open source projects. Company projects are the least popular choice.}
	}%
}
\vspace{0.5cm}

\subsection{RQ2: Are Stack Overflow answerers aware of outdated code in their answers?}

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.2cm]{0.98\textwidth}{%
		\textit{For research question 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them. Nonetheless, there are approximately 19\% of the answerers who rarely or never fix their outdated code.}
	}%
}
\vspace{0.5cm}

\subsubsection*{RQ2: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{How frequently did you check the software license of the code snippets you copy to Stack Overflow if they conflict with Stack Overflow's CC BY-SA 3.0 license? }
	}%
}
\vspace{0.5cm}

We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0. As shown in Figure~\ref{fig:survey_license_check}, approximately 69\% of answerers from both groups did not perform the checking. Nonetheless, they are about 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Do you have any other concerns regarding answering Stack Overflow with code snippets?}
	}%
}
\vspace{0.5cm}

We also invited the participants to give any comments regarding answering Stack Overflow with code snippets. These are some interesting comments we received.

Comment 1: ``The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software "professionals" that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.  A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about. Think php/mysql tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}). They're also full of toxic code snippets.''

Comment 2: ``When I copy code it's usually short enough to be considered "fair use" but I am not a lawyer or copyright expert so some guidance from SO would be helpful. I'd also like the ability to flag/review questions that violate these guidelines.''

Comment 3: ``My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.''

Comment 4: ``The main problem for me/us is outdated code, esp. as old answers have high google rank so that is what people see first, then try and fail. Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.''

Comment 5: ``Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).''

\subsubsection{Visitors' Experience}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How long have you been working on developing software?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{When you had a problem with your programming tasks, please rank in which order did you search for help (1 for the first, and 5 for the last, without a tie)?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently do or did you copy source code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Why did you copy and reuse code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Have you ever found any problems from reusing Stack Overflow code snippets?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you find problems from reusing Stack Overflow code snippets?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{What were the problems?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you report the problems back to the Stack Overflow discussion threads?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How did you report the problems?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Were you aware, at the time of copying the code, that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How often did you give attribution (adding a link to a Stack Overflow question/answer) as required by CC BY-SA 3.0 in the code where you used the snippet?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Have you ever checked if the Stack Overflow code snippet originated from a different source (e.g. an open source project) with an incompatible license to your project?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How often did you check for licensing conflicts of code snippets from Stack Overflow and your project(s) before using them?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you have legal problems by copying code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Could you please briefly explain what are the legal problems that you faced by copying code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Did you have any other problems from using code snippets from Stack Overflow?}
	}%
}
\vspace{0.5cm}

@@

\clearpage
\section{Appendix}
\appendix
\section{Stack Overflow Answerer Survey}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{answerer-1}
	\label{fig:answerer-1}
\end{figure}

@@

\section{Stack Overflow Visitor Survey}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\linewidth]{visitor-1}
	\label{fig:visitor-1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{visitor-2}
	\label{fig:visitor-2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{visitor-3}
	\label{fig:visitor-3}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{visitor-4}
	\label{fig:visitor-4}
\end{figure}

>>>>

\newcommand\fscore{\operatorname{F-score}}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{float}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{algorithm}
%\usepackage{cleveref}
\usepackage{algpseudocode}
\usepackage{pifont}
%\usepackage{cite}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{url}
%\usepackage{microtype}
\usepackage{caption}
\usepackage{booktabs} % For formal tables
\usepackage{subcaption}
\usepackage[misc,geometry]{ifsym} 
\usepackage{etoolbox}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}

@@

\author{Chaiyong~Ragkhitwetsagul, Jens~Krinke}

@@

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
%	\item \textbf{RQ4(Awareness of Stack Overflow visitors to outdated code):} \textit{Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
%	\item \textbf{RQ5 (Awareness of Stack Overflow visitors to software licensing conflicts):} \textit{Are Stack Overflow visitors aware of of software licensing conflicts caused by reusing code snippets from Stack Overflow?}
\end{enumerate}

\section{Research Methodology}
The study is performed using an online survey. We designed the survey using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. 
%We created two versions of the
%survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
The survey is completely anonymous and the participants could decide to leave at
any time. It does not collect any sensitive personal information from the
participants and were approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at UCL.  The complete version of
the survey can be found in the Appendix~\ref{appendixA}.

\subsection{The Survey Design}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions were mandatory while the other 9 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, experience of
answering Stack Overflow questions, sources of the Stack Overflow snippets,
concerns of copying code snippets to Stack Overflow, problems from code 
snippets on Stack Overflow, fixing outdated code, and additional feedbacks.

\subsection{Participants}

@@

@@

%\subsection{The Visitor Survey}
%
%The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
%questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
%questions. The first four questions were mandatory while the other 12 questions
%were shown to the participants based on their previous answers. The survey collects
%information of the participant's software development experience, importance of
%Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
%Stack Overflow snippets, licensing of code on Stack Overflow, and additional
%feedbacks.
%
%\begin{table}
%	\centering
%	\caption{The Stack Overflow visitors taken the survey}
%	\label{tab:visitors}
%	\begin{tabular}{lr}
%		\toprule
%		Invitation channels & Answers \\
%		\midrule
%		Chaiyong's Facebook post & 47 \\
%		Blognone.com & 32 \\
%		University of Molise & 6 \\
%		comp.lang.java.programmer & 3 \\
%		Software Engineering Facebook page & 1 \\
%		\midrule
%		Total & 89 \\
%		\bottomrule
%	\end{tabular}
%\end{table}
%
%The participants for this survey were invited to take the survey via five
%channels. The first channel is via the first author's Facebook post where the
%first author invited friends who are software developers and have experience of
%copying code snippets from Stack Overflow to take the survey. The second channel
%is a popular Thai technology news and media community called blognone.com which
%attracts a high number of software developers. The first author posted an
%invitation to the visitor survey in a discussion forum. The third channel
%collects answers from University of Molise which is the third author's
%workplace. The last two channels are from a comp.lang.java.programmer Google
%groups and Software Engineering Facebook page. The survey was open for
%participation for a month, from 25 July 2017 to 25 August 2017, before we
%collected and analysed the responses. The number of participants taken the
%survey are shown in Table~\ref{tab:visitors}.

@@

%\subsection{Answerer Responses}
We received 113 answers (38\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For RQ 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time. Other less popular choices include copying code from their personal projects, and open source projects. Company projects are the least popular choice.}
	}%
}
\vspace{0.5cm}

\subsubsection*{RQ2: Are Stack Overflow answerers aware of outdated code in their answers?}

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.2cm]{0.98\textwidth}{%
		\textit{For RQ 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them. Nonetheless, there are approximately 19\% of the answerers who rarely or never fix their outdated code.}
	}%
}
\vspace{0.5cm}

\subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}

@@

We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0. As shown in Figure~\ref{fig:survey_license_check}, 67.9\% -- 69\% of answerers from both groups did not perform the checking. There are only approximately 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For RQ3, approximately 60\% of answerers are aware of CC BY-SA 3.0 license enforced by Stack Overflow. However, 98--99\% of the answerers do not include software license in their Stack Overflow snippets nor check for licensing conflicts when they copy code snippets to Stack Overflow answers.}
	}%
}
\vspace{0.5cm}

In addition, we invited the answerers to give comments regarding their concerns when answering Stack Overflow (SO) with code snippets. Some interesting comments are selected and discussed belwo. The full set of answers can be found in the Appendix~\ref{appendixC}.

\begin{itemize}[label={}]
	\itemsep1em
	\item Comment 1: The answerer addresses a concern of reusing the code snippet without understanding. Moreover, he or she discusses a ramification of low-quality snippets or outdated code containing security issues.

	\begin{quote}\textit{The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software ``professionals'' that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.  A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about. Think PHP/MySQL tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}). They're also full of toxic code snippets.}\end{quote}

	\item Comment 2: The answerer suggests that a guidance from Stack Overflow regarding software license will be beneficial.

	\begin{quote}\textit{When I copy code it's usually short enough to be considered ``fair use'' but I am not a lawyer or copyright expert so some guidance from SO would be helpful. I'd also like the ability to flag/review questions that violate these guidelines.}\end{quote}

	\item Comment 3: The answerer addresses a concern of code understanding.

	\begin{quote}\textit{My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.}\end{quote}

	\item Comment 4: The answerer discusses a problem from outdated code and his/her solution.

	\begin{quote}\textit{The main problem for me/us is outdated code, esp. as old answers have high Google rank so that is what people see first, then try and fail. Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.}\end{quote}

	\item Comment 5: The answerers gives insights into the quality of the Stack Overflow code snippets.

	\begin{quote}\textit{Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).}\end{quote}
\end{itemize}

%\subsection{Visitor Responses}
%
%To answer RQ4 and RQ5, we ask Stack Overflow visitors about their experiences of outdated code and their awareness to software license of Stack Overflow code snippets. We received 89 answers from 5 groups of Stack Overflow visitors. The combined results and discussions are presented below.
%
%\subsubsection*{RQ4: Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
%
%We asked the visitors whether they have any problem from reusing Stack Overflow code snippets and how often did the problems occur. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.5\linewidth]{survey_v_problems}
%	\caption{Number of visitors who experienced a problem from reusing Stack Overflow code snippets.}
%	\label{fig:survey_v_problems}
%\end{figure}
%
%
%\vspace{0.5cm}
%\noindent\fbox{%
%	\parbox[c][0.5cm]{0.98\textwidth}{%
%		\textit{For RQ4, }
%	}%
%}
%\vspace{0.5cm}
%
%\subsubsection*{RQ5: Are Stack Overflow visitors aware of software licensing of code snippets from Stack Overflow?}
%
%\vspace{0.5cm}
%\noindent\fbox{%
%	\parbox[c][0.5cm]{0.98\textwidth}{%
%		\textit{For RQ5, }
%	}%
%}
%\vspace{0.5cm}

@@

\clearpage
\section{Appendix}

This appendix contains additional materials of the Stack Overflow answerer survey questions, the visitor survey questions, and the complete set of open comments from the Stack Overflow answerers.

\clearpage

\appendix
\section{Stack Overflow Answerer Survey}\label{appendixA}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{answerer-1}
	\label{fig:answerer-1}
\end{figure}

@@

%\section{Stack Overflow Visitor Survey}\label{appendixB}
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.85\linewidth]{visitor-1}
%	\label{fig:visitor-1}
%\end{figure}
%
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.9\linewidth]{visitor-2}
%	\label{fig:visitor-2}
%\end{figure}
%
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.9\linewidth]{visitor-3}
%	\label{fig:visitor-3}
%\end{figure}
%
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.9\linewidth]{visitor-4}
%	\label{fig:visitor-4}
%\end{figure}

\section{Open Comments from Stack Overflow Answerers}\label{appendixC}

\begin{enumerate}
	\itemsep1em
	\item Sometimes you have to post code from official documentation, like in case of C\#, code form MSDN is posted in the answer with added explanation.
	\item Snippets on SO are usually for demonstrating a technique and therefore age well. If otherwise, I usually made them a gist, codebin or jsfiddle.
	\item The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software ``professionals'' that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.
	\item A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about. Think PHP/MySQL tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}). They're also full of toxic code snippets.
	\item Just to say: the reason that I very rarely check the license status is that the code I am posting is almost always my own or adapted from the question, or imported from an open source project that I have worked on and already know the license terms, or from my own company code that I can 100\% say it is OK to post in public because I know our policies.
	\item No. Code snippets are short and small enough that no IP can be in them.
	\item The point of snippets are that they are trivial. I mostly write from scratch or copy-\&-fix a snippet from the question. Most are illustrative or incomplete --- they aren't of any value at all in isolation. They rarely take more than a few minutes to write, and it's usually harder to explain what they're doing in plain English. Where something is large enough to worth the effort of licensing then it's far too big for a snippet. In those cases I create a GitHub project (with a license) and link to it. I'd be wary of increased IP controls --- I doubt there is value they could add to snippets, but they could create significant barriers to contributors, which would hurt the site.
	\item I always try to see what kind of person is asking the question. If it is a student, I don't want to just hand out the answer; they will learn nothing from that. If, on the other hand, it's somebody looking for best practices or a clever trick, I'm not too worried about giving out the solution. In this case, chances are much higher that the person asking the question will go ``Ahh, yes, of course!'' and understand the question, whereas some students are more likely to mindlessly copy-paste the answer.
	\item However, it is also a competitive site, so if your answer requires too much work to incorporate, it won't get accepted or upvoted. As a result, some people---I'm guilty of this myself, I'm sure---will hand out an answer willy-nilly that might solve the problem at hand, but in the long run be a disservice to the person asking.
	\item But I digress: My point is that it's sometimes better to describe a solution rather than just hand off a code snippet. However, since your project seems to pertain to copyright issues, I suppose that's not relevant to you.
	\item I'm not sure it's possible to include a license in your questions/answers. I'm not sure what the legal ramifications would be if you tried it, since you already agreed to S.O.'s terms. This is a very interesting question and I look forward to hearing the results of your research.
	\item I think it's important to realise the code snippets are designed to be very small, useful to illustrate concepts (10 lines or less). When you consider licensing laws of such a small amount of code, while technically may be violating a licence, in practice it would be nearly impossible to enforce such a claim.
	\item SO code snippets are great but there is lot to improve . It's hard to edit and see output in so but website like jsfiddle , jsbin provide nice interface where code editing and output is easy to do.
	\item Outer thing is in so lot of code snippets doesn't work because some users don't add libraries like angular, jquery. I think it's better if we can identify and ask user to auto inject relevant libraries.
	\item Code snippets are usually just a few lines of code so it will be hard to enforce any copyright claims except when it is a method used for something company-specific (such as generating encryption keys). Regardless, since most of the code I write is specifically to answer a given question and having full knowledge of the license system used by Stack Overflow, it is entirely unimportant to concern myself with licensing the code provided. Also, code from MSDN documentation which I sometimes adapt and modify for answers are already in the public domain so it makes no sense re-licensing it.
	\item On the matter of deprecation, I almost entirely use .NET which has got different versions of the framework. Therefore, code deprecation is not often a problem since what is deprecated on one version of the framework may be the only way of solving a given problem on an older version of the framework. I may also have to add that questions I tend to answer are about how to solve general coding problems so they are not usually subject to deprecation.
	\item I think you're forgetting the fact that as a community, we want to share knowledge. Patents, copyright issues and so on --- it's all just annoying. We're there to have fun and to share knowledge with people. 
	\item In the early days, the internet used to be full of free-for-all stuff without any licenses. Because of that, it was a fantastic tool to share knowledge and information on a vast scale. The remnant of this, open source, couldn't have existed without this!
	\item Personally, I believe this ``intellectual property'' drive of the last decade is completely overrated. If you make something \textbf{substantial}, it's fine to be able to claim some ownership --- but on snippets? It's like patenting the stuff you make in your free time in your shed... it doesn't make sense and just adds to the pile of legal bullshit imho.
	\item No. I only put code on there that I have the right to (code I created or have permission to share). Adding the code is not an issue for me.
	\item When I copy code it's usually short enough to be considered ``fair use'' but I am not a lawyer or copyright expert so some guidance from SO would be helpful. I'd also like the ability to flag/review questions that violate these guidelines.
	\item The snippets are all small enough that I reckon they fall under fair use.
	\item I always try and attribute the code I take from other places. I feel pointing back to the origin should be sufficient in terms of giving credit where it's due. Open source is about the sharing of ideas so that others can build on them. Education is a primary use case of open source in my opinion.
	\item My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.
	\item This survey may be inapplicable to me because I never copy code from existing projects.
	\item Stack Overflow did an effort to apply a MIT license to all code snippets, while keeping CC-SA for the text content. Too bad they didn't succeed with it, as it would have solved many issues.
	\item The main problem for me/us is outdated code, esp. as old answers have high Google rank so that is what people see first, then try and fail. Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.
	\item I've got no issues with code snippets on Stack Overflow, I think they are great. Any one using them should pay attention to details such as the date of the answer etc.
	\item SO's license is not clearly explained when one registers or starts to answer questions.
	\item No, most copied code snippets are so trivial that licensing them would be nearly impossible. It's also mostly modified version, where only some patterns are used.
	\item Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).
	\item I think most example and explanatory snippets don't need a code-specific license. The CC license provides just fine. The examples either aren't copyrightable in the first place, or merely used as starting point (not used exactly as-is, not very different from reading an ``All rights reserved'' education book when learning programming, and ``using'' it in your career every day going forward). In addition, there is also the attitude of authors. Where I might care about attribution for distribution of my answer, the code within my answer is always Public Domain for me, meaning, I would never defend it. (I used to state that on my profile as well, but not in every post.)
	\item Correctness and even syntax are often in doubt if I haven't had time to test the snippet end-to-end under the OP's conditions/environment.
	\item It will be awesome if it becomes simple git repositories like github's gist.
	\item Note that although I was not specifically of SO's licensing terms, I did have an in mind what those terms were likely to be. I have always made sure that there should be no reason that I should not share the code that I included in my replies.
	\item It's an ESSENTIAL part of the site, it would NEVER work without such pieces of code. Also, given the snippets are very small in 99.99\% of cases, legal aspects of this are inherently and pretty much always overlooked by the users.
\end{enumerate}
